Data Processing

### 2024-02-21 R/processing-code/Processing-Quarto-Output.qmd

```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('processing-code/creating-df/Creating_Data_Frame.R')
```

```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('R/processing-code/Cleaning Data/cleaning1.R')
```

@@

```{r, cleandata1}
```

@@

>>>>

```{r, include=FALSE, cache=FALSE}
library(here)
knitr::read_chunk(here("./R/processing-code/creating-df/Creating_Data_Frame.R"))
```

@@

```{r, cleandata}

```

@@

```{r, include=FALSE, cache=FALSE}
library(here)
knitr::read_chunk(here("./R/processing-code/cleaningdata/cleaning1.R"))
```

```{r, packages2}
```
